miniKanren with fair search strategies

### 2019-05-21 Paper/paper.tex
rewrite abstract

The syntax of a programming language should reflect its semantics. When writing 
a \conde{} expression in miniKanren, a programmer would expect all clauses 
share the same chance of being explored, as these clauses are written in 
parallel. The existing search strategy, interleaving depth-first search 
(\DFSi{}), 
however, prioritizes its clauses by the order how they are written down. 
Similarly, when a \conde{} is followed by another goal conjunctively, a 
programmer would expect states in parallel share the same chance of being 
explored. Again, the answers by \DFSi{} is different from the 
expectation. We have devised three new search strategies that have different 
level of fairness in \disj{} and \conj{}.

\NOTE[LKC]{\disj{} and \conj{} occurs free in the abstract.}

>>>>

We describe fairness levels in disjunction implementation and conjunction 
implementation. Specifically, a disjunction implementation can be fair, 
almost-fair, or unfair. And a conjunction implementation can be fair or unfair. 
We compare the fairness level of four search strategies: interleaving 
depth-first search (DFSi), balanced interleaving depth-first search (DFSbi), 
fair depth-first search (DFSf), and breadth-first search (BFS). DFSi is one of 
the best-understood search strategies in miniKanren community. DFSbi and DFSf 
are new. And we present a new implementation of BFS. We demonstrate by a 
quantitative evaluation that DFSbi and DFSf are competitive alternatives to 
DFSi, and that BFS is less practical.

% The syntax of a programming language should reflect its semantics. When writing 
% a \conde{} expression in miniKanren, a programmer would expect all clauses 
% share the same chance of being explored, as these clauses are written in 
% parallel. The existing search strategy, interleaving depth-first search 
% (\DFSi{}), 
% however, prioritizes its clauses by the order how they are written down. 
% Similarly, when a \conde{} is followed by another goal conjunctively, a 
% programmer would expect states in parallel share the same chance of being 
% explored. Again, the answers by \DFSi{} is different from the 
% expectation. We have devised three new search strategies that have different 
% level of fairness in \disj{} and \conj{}.
% 
% \NOTE[LKC]{\disj{} and \conj{} occurs free in the abstract.}
